\documentclass[11pt]{article}


\usepackage{geometry}
\geometry{a4paper}


\begin{document}
\title{ {\Huge \textbf{EDUCATIONAL INSITUTIONS DATABASE}}}
\maketitle
\begin{large}
\begin{Large}
{\LARGE System Requirements Specification}
\end{Large}
\end{large}
 
\section{Introduction}
{{\large This is a web application which maintains and updates various information regarding each educational institution.}}
\section{Purpose}
{\large
 It is very useful for people who are new to a place to search for schools and colleges nearby suiting their own necessities.}
 \\ \\{\large It is a one-stop destination for users who want information during admissions as well as for students to be updated about all the events happening in different colleges.}
\section{Scope}
{\large It has a database server supporting information about hundreds of              institutions.}
\\ {\large Information includes:
\begin{itemize}
\item Address
\item Contact details
\item Admission process/status
\item Faculty and student achievements
\item Cut-offs
\item Placements
\item Projects
\item News updates
\item College maps(internal)
\item Financial aid
\item Links to website and social media accounts

\end{itemize}


 Address,contact details,Admission process/status,faculty and student achievements,cut-offs,placements,projects,news updates,college map(internal), financial aid and links to website and social media pages.}
\\ {\large Several search filters avaiilable based on ranking,department,location,college name,hostel facility,Alumni etc.}
\\\begin{large}
 Notifications about upcoming events in various educational institutions like visits by industry professionals,workshops,college fest,sports events etc.               
\\It can be accessed through android devices by app as well as the internet both in mobile phones as well as desktops.


\end{large}
  
\section{DESCRIPTION}

\begin{large}
The application we are going to create has various factors by which comparision of different colleges is made easier.
\\ \\The application opens with a registration page with emailid/Phno,name, occupation and a password to be entered for future login. 
\\ \\The comparision and sorting factors are:
\begin{itemize}
\item College name
\item Type(Govt / Pvt)
\item Admission mode(Through mains/Advanced/Individual test/Sports quota)
\item Hostel facility
\item Location
\item Cut-offs for each department
\item Placements
\item Alumni
\item Faculty
\end{itemize}
 
These factors are given as options in sortby drop down option in every page so that multiple filters can be implemented.
\\ \\According to the constraints,the profiles of various colleges are displayed giving 
priority in order of
\begin{enumerate}
\item Search by the user
\item Cut-offs
\item Rankings
\item Total no of seats for each branch.

\end{enumerate}

The display of the profile contains two options namely
\begin{itemize}
\item Add to BASKET
\item View complete info
\end{itemize}
The colleges of interest of the user can be added to a new page(like a BASKET) after viewing the profiles and grouped according to the user's needs.It can be accessed through login.
\\ The page containing complete information regarding the institute can be accessed from the main page as well as the basket.
\\ \\The complete information includes all the sorting factors mentioned above and as well as additional information like
\begin{itemize}
\item Student faculty ratio
\item Faculty experience
\item Percent placed
\item Percent pursuing higher education
\item Internship opportunities
\item Student exchange programs

\end{itemize}
   
 The respective college website links to various other necessary information are provided.
\\ \\Updates are notified in a separate page especially  about different events in each college and details its and notifications are sent to the email/phno provided at the time of login. 
\\The website can be accessed by many people at a time and outline made to be easily understood by all.
\\ \\The services can be provided to all educational institutions including schools,medical colleges,colleges offering Mtech,Mdes,phd in engineering and other streams.\\ \\

                               \author{\textit{\textbf{COE16B013}}}   
                               \\ \author{\textit{\textbf{COE16B014}}}
                               \\ \author{\textit{\textbf{COE16B022}}}
                                

\end{large}
\end{document}
